Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-01-16 2024pipit/figures/core-structure.tex
rework missing proof obligations prose

%!TEX root = ../Main.tex
\begin{figure}
  \includegraphics[width=\textwidth]{figures/core-structure.pdf}
\caption{Architecture of Pipit. The gray boxes and solid arrows are defined in this paper. The white boxes and dashed arrows are trusted components. The labels next to the arrows denote properties of the translation. The refinement label ($\subseteq$) indicates a verified abstraction relation; the negated entailment ($\not\vdash$) indicates that the entailment relation --- contracts and checked properties proven on abstract system apply to the checked semantics --- is not yet verified; the equivalence ($=$) denotes a verified equivalence relation.}
\label{f:core:structure}
\end{figure}

>>>>

%!TEX root = ../Main.tex
\begin{figure}
  \includegraphics[width=\textwidth]{figures/core-structure.pdf}
\caption{Architecture of Pipit. The gray boxes and solid arrows are defined in this paper. The white boxes and dashed arrows are trusted components. The labels next to the arrows denote properties of the translation.
% The refinement label ($\subseteq$) indicates a verified abstraction relation; the negated entailment ($\not\vdash$) indicates that the entailment relation --- that the proof obligations on the abstract transition system entail the original proof obligations --- is not yet verified; the equivalence ($=$) denotes a verified equivalence relation.
}
\label{f:core:structure}
\end{figure}

### 2024-01-16 2024pipit/section/30-Core.tex
rework missing proof obligations prose

\autoref{f:core:structure} shows the architecture of Pipit.
On the left-hand-side, the surface syntax embedded in \fstar{} is shown; this includes some Pipit-specific syntactic sugar.
The translation from the surface syntax to the core language is trusted.
There are two targets from the core language: abstract transition systems for verification, and executable transition systems for extraction to C.
The translation from the abstract systems is verified to be an abstraction according to the dynamic semantics (\autoref{s:core:dynamic}).
One property that still remains to be proven is that if the abstract transition system says a contract or checked property holds, then the same contract or property holds on the original semantics; this is denoted as negated entailment in the figure ($\not\vdash$).
The translation to executable transition system is proven to be semantics preserving, as is the subsequent translation to \lowstar{}.
The translation from \lowstar{} to C is external to this paper and forms part of our trusted computing base.

>>>>

\autoref{f:core:structure} shows the high-level architecture of Pipit.
On the left-hand-side, the surface syntax embedded in \fstar{} is shown; this includes some Pipit-specific syntactic sugar.
The translation from the surface syntax to the core language is trusted.
There are two targets from the core language: abstract transition systems for verification, and executable transition systems for extraction to C.
The translation from the abstract systems is verified to be an abstraction according to the dynamic semantics (\autoref{s:core:dynamic}).
One property that still remains to be proven is that the proof obligations on the abstract transition system entail the original proof obligations (\autoref{s:transition}); this pending proof is denoted as negated entailment in the figure ($\not\vdash$).
The translation to executable transition system is proven to be semantics preserving, as is the subsequent translation to \lowstar{}.
The translation from \lowstar{} to C is external to this paper and forms part of our trusted computing base.
